Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
Added a todo to remind us to try to add more to the mechanizing section.

    Proving our own version of Lemma~\ref{lem:soundness} actually turned out to
    be instructive because it forced us to recognize that the original
    formulation in Simonet and Pottier's paper on \origLang~\cite{InfoFlowML}
    wasn't exactly correct as stated.  Specifically, it is entirely possible
    that a step in the operational semantics does not translate to a step in the
    operational semantics under either projection, as in the case of the
    \ref{eq:lift-app} rule, where $\lift{e}_i$ and $\lift{e'}_i$ are identical.
    Luckily, we are fairly confident, given that we were still able to prove
    Lemma~\ref{lem:stuck_bracket} despite this change, that this is not a
    critical error in the original paper.
\end{description}

>>>>

    Proving our own version of Lemma~\ref{lem:soundness} actually turned out to
    be instructive because it forced us to recognize that the original
    formulation in Simonet and Pottier's paper on \origLang wasn't exactly
    correct as stated.  Specifically, it is entirely possible that a step in the
    operational semantics does not translate to a step in the operational
    semantics under either projection, as in the case of the \ref{eq:lift-app}
    rule, where $\lift{e}_i$ and $\lift{e'}_i$ are identical.  Luckily, we are
    fairly confident, given that we were still able to prove
    Lemma~\ref{lem:stuck_bracket} despite this change, that this is not a
    critical error in the original paper.
\end{description}

\todo{more?}
